Abstractions for Type-Level Programming

### 2022-04-08 article.tex
Define Ψ and Ξ in figure caption

% TODO: define Ψ and Ξ
% TODO: cite the precise figure in Pierce 2002
\FMSyntaxEvaluation{\SystemFm syntax and evaluation rules for a given set of classes $\C$ with class inheritance $\Ψ$ and class disjointness $\Ξ$. \hl{\text{Highlights}} correspond to additions to \SystemFsub.}

\FMTypingRules{\SystemFm type system for a given set of classes $\C$ with class inheritance $\Ψ$ \\and class disjointness $\Ξ$. \hl{\text{Highlights}} correspond to additions to \SystemFsub.}

>>>>

\FMSyntaxEvaluation{\SystemFm syntax and evaluation rules for a given set of classes $\C$ with class inheritance $\Ψ$. The $\Ψ$ relation is a partial order on $\C$ that describes the inheritance between classes. \hl{\text{Highlights}} correspond to additions to \SystemFsub, as per \citep[Figure 26-1]{pierce2002types}.}

\FMTypingRules{\SystemFm type system for a given set of classes $\C$ with class inheritance $\Ψ$ and class disjointness $\Ξ$. $\Ψ$ is a partial order on $\C$ that describes the inheritance between classes. $\Ξ$ is symmetric relation over $\C$ that relates classes which share no inhabitants. \hl{\text{Highlights}} correspond to additions to \SystemFsub, as per \citep[Figure 26-1]{pierce2002types}.}
